Methods for Large Scale Learning to Rank

### 2014-09-24 report/Chapters/Introduction.tex
beter

\section{Research Goals}
\label{sec:goals}
The objective of this thesis is to explore the speed-up in execution time of Learning to Rank algorithms through parallelisation using the MapReduce framework.
This work focuses on those Learning to Rank algorithms that have shown leading performance on relevant benchmark data sets.
This thesis addresses the following research questions:
\begin{description}
\item[RQ1] What are the best performing Learning to Rank algorithms in terms of accuracy on relevant benchmark data sets?\\

>>>>

\section{Research Goals}
\label{sec:goals}
The objective of this thesis is to explore the speed-up in execution time of Learning to Rank algorithms through parallelisation using the MapReduce computational model. The set of Learning to Rank models described in literature is of such size that it is infeasible to conduct an exhaustive experiment on all Learning to Rank models. Therefore we set the scope of our scalability experiment to include those Learning to Rank algorithms that have shown leading performance on relevant benchmark data sets.
This thesis addresses the following research questions:
\begin{description}
\item[RQ1] What are the best performing Learning to Rank algorithms in terms of ranking accuracy on relevant benchmark data sets?\\
